%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Manager, Planning \& Operations, BC Mobile Medical Unit} % Job title
    {Provincial Health Services Authority (PHSA)} % Organization
    {Vancouver, BC} % Location
    {July 2018 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Monitors and enhances the strategic operational plan, program budgets, identifying areas for program growth and continuous improvement, along with appropriate implementation strategies.}
        \item {Applies LEAN project management methodology to project-based program initiatives, including identification and engagement of key stakeholders, development of detailed project proposals, objectives, and work plans.}
        \item {Monitors and reports on the status of program initiatives and major barriers encountered. Tracks progress of these initiatives according to key performance indicators by collating, measuring, and assessing the metrics for reporting purposes.}
        \item {Responsible to create and maintain the programs’ communication tools/methods and social media business plan to ensure effective channels are in place and to enhance profile of the MMU as a provincial service - including accountability and oversight of the program’s web and social media presence; building and delivering presentations.}
        \item {Acts as a key support for all members of the MMU team (core team, as well as casual clinical pool, and team of medical directors); provides direct supervision to the program’s Administrative Assistant; and works in conjunction with the Facility and Clinical Managers to ensure day-to-day, as well as deployment requirements for the MMU are being met. Functions as the Lead for Communications and IT issues requiring collaboration and resolve with the required departments.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Coordinator, BC Mobile Medical Unit} % Job title
    {Provincial Health Services Authority (PHSA)} % Organization
    {Vancouver, BC} % Location
    {September 2016 - July 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engage with internal and external stakeholders to lead the planning and execution of deployments/events of varying sizes across the province (up to six per year).}
        \item {Lead program communications including advisory committee updates, key program messaging, media relations on deployment, issues management and program communications plan.}
        \item {Work can be outside of regular work hours and on short notice; Being able to adapt quickly and produce solutions for unusual problems or requests is central to team effectiveness.}
       \item {Gathering and reviewing qualitative and quantitative data analysis of each deployment, providing feedback for meaningful program improvement for future endeavours.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Administrator, Diagnostic Accreditation Program} % Job title
    {College of Physicians \& surgeons of British Columbia } % Organization
    {Vancouver, BC} % Location
    {July 2013 - August 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Project lead on certificate process, providing workflow charts, timelines, and researching policies}
        \item {Assist in the recruitment and on-boarding orientation of physician and technical surveyors, maintaining survey schedules, and editing 5-10 reports biweekly.}
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
    {Assistant, Complaints \& Practice Investigations} % Job title
    {College of Physicians \& surgeons of British Columbia } % Organization
    {Vancouver, BC} % Location
    {February 2012 - July 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Case managing 300+ complaints annually, gathering and disseminating medical correspondence to internal and external parties under a time-sensitive HPA process.}
        \item {Professional communication with medical staff, triaging information and providing tactful answers to complex health related issues with special interest in physician conduct and advertising.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
